Summary of Changes in response to Referee's Report

### 2016-01-01 curves-write-up/AIF/changes-summary.tex
curves: add some response to e_i -> s_i suggestion

\begin{enumerate}
	\item We added a remark on Gorensteinness of the log canonical ring following
	the definition of a log spin canonical ring in the background section.
	We noticed in comment 1 that the referee made a comment saying
	``Cohen-Macaulay and
projectively Gorenstein follows as usual (of course, provided there are
no log canonical points).'' We were a bit confused about the parenthetical, but interpreted
it to mean that the canonical ring may not be Gorenstein if it is of the form
\begin{align*}
	\oplus_n H^0(X, P + n L)
\end{align*}
for $L$ some fractional divisor and $P$ a point. Of course, in our paper, all canonical rings are of the form
\begin{align*}
	\oplus_n H^0(X, n L)
\end{align*}
for $L$ a fractional divisor, so this would not pose an issue.
	\item Use Hilbert polynomial in Example $\_\_\_$
	\item Replace ``best lower approximation'' with Hirzebruch--Jung
		fractions
	\item (Not to-do yet) Change notation from $\frac{e_i - 1}{2 e_i}$
		to $\frac{e'_i}{2 e'_i + 1}$ where $e'_i = \frac{e_i - 1}{2}$ and
		we range over all $e'_i$ instead of odd $e_i$.
\end{enumerate}

>>>>

\begin{enumerate}
	\item We added a remark on Gorensteinness of the log canonical ring following
	the definition of a log spin canonical ring in the background section.
	We noticed in comment 1 that the referee made a comment saying
	``Cohen-Macaulay and
projectively Gorenstein follows as usual (of course, provided there are
no log canonical points).'' We were a bit confused about the parenthetical, but interpreted
it to mean that the canonical ring may not be Gorenstein if it is of the form
\begin{align*}
	\oplus_n H^0(X, P + n L)
\end{align*}
for $L$ some fractional divisor and $P$ a point. Of course, in our paper, all canonical rings are of the form
\begin{align*}
	\oplus_n H^0(X, n L)
\end{align*}
for $L$ a fractional divisor, so this would not pose an issue.
	\item Use Hilbert polynomial in Example $\_\_\_$
	\item Replace ``best lower approximation'' with Hirzebruch--Jung
		fractions
\end{enumerate}

\section{Other suggestions}
The referee also made the following suggestions.

\begin{enumerate}
	\item Change notation from $\frac{e_i - 1}{2 e_i}$
		to $\frac{s_i}{2 s_i + 1}$ where $s_i = \frac{e_i - 1}{2}$ and
		we range over all integers $s_i$ instead of odd integers $e_i$.
\end{enumerate}

We decided not to implement the above suggestions for the following
reasons, respectively.

\begin{enumerate}
	\item Firstly, we maintained the $e_i$ notation for consistency
	with the notation established in Voight--Zureick-Brown. These
	$e_i$ correspond to the stabilizer orders in the log spin
	canonical ring case considered there. Furthermore, we often
	list degrees of generation and relations enumerated by signatures
	of the form $(g; e_1, \ldots, e_n; \delta)$ with bounds given in
	the	form $\min(5, e_1, \ldots, e_n)$ which are more natural to
	consider than enumeration by signatures $(g; s_1, \ldots, s_n;
	\delta)$ with bounds given in the form $\min(5, 2s_1 + 1, \ldots,
	2s_n + 1)$.
\end{enumerate}
